### 2019-09-12 reports/thesis/chapters/3_compoundPoisson.tex
Add and adjust bib

The variance of the M step estimators can be obtained by using the Cram\'er-Rao lower bound \citep{rao1945information, cramer1946mathematical} from the Fisher's information matrix defined as
\begin{equation}
  \matr{I} = -\expectation\left[
    \nabla_{\lambda,\alpha,\beta}\nabla_{\lambda,\alpha,\beta}\T \ln L(\lambda,\alpha,\beta;X,Y)
  \right]
\end{equation}
where
\begin{equation}
  \nabla_{\lambda, \alpha,\beta}=
  \begin{pmatrix}
    {\partial}/{\partial \lambda}
    \\
    {\partial}/{\partial \alpha}
    \\
    {\partial}/{\partial \beta}
  \end{pmatrix}
  \ .
\end{equation}
The calculation is similar to the derivatives of $T$ using the same approximations. Using the fact that $\expectation[Y]=\lambda$ and another approximation $\expectation\left[\psi^{(r)}(\alpha Y)\right]\approx\psi^{(r)}(\alpha \lambda)$, then
\begin{equation}
  \matr{I}=
  \begin{pmatrix}
    \dfrac{n}{\lambda} & 0 & 0 \\
    0 & (\lambda^2+\lambda)\psi'(\alpha\lambda)+2\alpha\lambda^2\psi''(\alpha\lambda)+\frac{1}{2}\alpha^2\lambda^3\psi'''(\alpha\lambda) & -\dfrac{n\lambda}{\beta}\\
    0 & -\dfrac{n\lambda}{\beta} & \dfrac{n\alpha\lambda}{\beta^2}
  \end{pmatrix}
  \ .
\end{equation}
The Cram\'er-Rao lower bound is then
\begin{equation}
  \cov\left[
    \begin{pmatrix}
      \widehat{\lambda}\\\widehat{\alpha}\\\widehat{\beta}
    \end{pmatrix}
  \right]
  =
  \matr{I}^{-1}
  \ .
\end{equation}

>>>>

The variance of the M step estimators can be obtained by using the Cram\'er-Rao lower bound \citep{rao1945information, cramer1946mathematical} from the Fisher's information matrix \citep{fisher1922on} defined as
\begin{equation}
  \matr{I} = -\expectation\left[
    \nabla_{\lambda,\alpha,\beta}\nabla_{\lambda,\alpha,\beta}\T \ln L(\lambda,\alpha,\beta;X,Y)
  \right]
\end{equation}
where
\begin{equation}
  \nabla_{\lambda, \alpha,\beta}=
  \begin{pmatrix}
    {\partial}/{\partial \lambda}
    \\
    {\partial}/{\partial \alpha}
    \\
    {\partial}/{\partial \beta}
  \end{pmatrix}
  \ .
\end{equation}
The calculation is similar to the derivatives of $T$ using the same approximations. Using the fact that $\expectation[Y]=\lambda$ and another approximation $\expectation\left[\psi^{(r)}(\alpha Y)\right]\approx\psi^{(r)}(\alpha \lambda)$, then
\begin{equation}
  \matr{I}=
  \begin{pmatrix}
    \dfrac{n}{\lambda} & 0 & 0 \\
    0 & (\lambda^2+\lambda)\psi'(\alpha\lambda)+2\alpha\lambda^2\psi''(\alpha\lambda)+\frac{1}{2}\alpha^2\lambda^3\psi'''(\alpha\lambda) & -\dfrac{n\lambda}{\beta}\\
    0 & -\dfrac{n\lambda}{\beta} & \dfrac{n\alpha\lambda}{\beta^2}
  \end{pmatrix}
  \ .
\end{equation}
The Cram\'er-Rao lower bound is then
\begin{equation}
  \cov\left[
    \begin{pmatrix}
      \widehat{\lambda}\\\widehat{\alpha}\\\widehat{\beta}
    \end{pmatrix}
  \right]
  =
  \matr{I}^{-1}
  \ .
\end{equation}

### 2019-09-12 reports/thesis/chapters/4_variancePrediction.tex
Add and adjust bib

This section describes how forward stepwise selection \citep{friedman2001elements} was used to select which polynomial features to use in the systematic component.

In summary, forward stepwise selection fits a basic model to the data initially. A feature is added to make the model more complicated at each step to improve the fit onto the data. This is continued until the model cannot be improved subject to overfitting. The Akaike information criterion (AIC) \citep{friedman2001elements} and the Bayesian information criterion (BIC) \citep{friedman2001elements} are criteria which can be used to assess the fit of the model at each step without overfitting to the data too much.

>>>>

This section describes how forward stepwise selection \citep{efroymson1960multiple, friedman2001elements} was used to select which polynomial features to use in the systematic component.

In summary, forward stepwise selection fits a basic model to the data initially. A feature is added to make the model more complicated at each step to improve the fit onto the data. This is continued until the model cannot be improved subject to overfitting. The Akaike information criterion (AIC) \citep{akaike1974new, friedman2001elements} and the Bayesian information criterion (BIC) \citep{schwarz1978estimating, friedman2001elements} are criteria which can be used to assess the fit of the model at each step without overfitting to the data too much.
